\Large UC President's Postdoctoral Fellowship Research Statement \\ \textbf{How Unique is the Solar System? Planetary Luminosities as Fingerprints for the Origins and Properties of Exoplanets}

### 2017-06-15 Postdoc Applications/AnaMariaPisoResume.tex
upd

\begin{list2}
\item[] {\bf The Role of Ice Compositions and Disk Dynamics for Snowlines and the C/N/O Ratios in Active Disks} \\
AAS Inner Solar Systems Meeting, Austin, TX, June 2017\\
Invited talk \\
\end{list2}

>>>>

\begin{list2}
\item[] {\bf The Role of Ice Compositions and Disk Dynamics for Snowlines and the C/N/O Ratios in Active Disks} \\
AAS Inner Solar Systems Meeting, Austin, TX, June 2017\\
\end{list2}
